---
title: "Reports, Tables & Maps"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    theme: cosmo
    css: _styles.css
---

---


**NWB Reports**

<ul>
<li>Main report - [Download PDF](downloads/main_report/BEACONs_benchmark_report.pdf)</li>
<li>All ecoregion reports - [Download ZIP](downloads/eco_report/Eco_results_final.zip)</li>
<li>MDR analysis - [Download PDF](downloads/mdr_report/BEACONs_mdr_report.pdf)</li>
<li>Focal species report - [Download PDF](downloads/focal_species_report/BEACONs_focal_species_report.pdf)</li>
<li>Focal species appendix A: Review of management plans - [Download PDF](downloads/focal_species_report/Appendices/Appendix_A_bibliography_mgmt_plans.pdf)</li>
<li>Focal species appendix B: Management plans goals & targets - [Download XLSX](downloads/focal_species_report/Appendices/Appendix_B_mgmt_plans_goals&targets.xlsx)</li>
<li>Focal species appendix C: Experts consulted - [Download PDF](downloads/focal_species_report/Appendices/Appendix_C_experts_consulted.pdf)</li>
<li>Focal species Appendix D: Summary of datasets - [Download XLSX](downloads/focal_species_report/Appendices/Appendix_D_focal_species_data.xlsx)</li>
</ul>

**NWB Datasets:**

<ul>
<li>Benchmark networks metadata - [Download PDF](downloads/BEACONs_metadata_shapefiles.pdf)</li>
<li>NWBLCC-level Shapefiles (e.g., ecoregions) - [Download ZIP](downloads/nwblcc_ecoregions.zip)</li>
<li>Hydrology Units HUC8 and FDA - [Download ZIP](downloads/nwblcc_fdahuc8.zip)</li>
</ul>

**NWB Biophysical Criteria Datasets (all ecoregions):**

<ul>
<li>Climate moisture index - [Download ZIP](downloads/nwb_datasets/cmi.zip)</li>
<li>Gross primary productivity - [Download ZIP](downloads/nwb_datasets/gpp.zip)</li>
<li>Lake edge density - [Download ZIP](downloads/nwb_datasets/led.zip)</li>
<li>North American Landcover 2010 - [Download ZIP](downloads/nwb_datasets/nalc.zip)</li>
</ul>

**NWB Climate Change Datasets (all ecoregions):**

<ul>
<li>Climatic velocity (forward and backward) - [Download ZIP](downloads/nwb_datasets/climatic_velocity.zip)</li>
<li>Climatic velocity PCAs (temperature and precipitation) - [Download ZIP](downloads/nwb_datasets/climatic_velocity_pca.zip)</li>
</ul>

**NWB Focal Species Datasets (all ecoregions):**

<ul>
<li>Caribou - [Download ZIP](downloads/nwb_datasets/caribou.zip)</li>
<li>Caribou ranges - [Download ZIP](downloads/nwb_datasets/caribou_ranges.zip)</li>
<li>Moose - [Download ZIP](downloads/nwb_datasets/moose.zip)</li>
<li>Dall / Thinhorn Sheep - [Download ZIP](downloads/nwb_datasets/sheep.zip)</li>
<li>Beaver - [Download ZIP](downloads/nwb_datasets/beaver.zip)</li>
<li>Chinook Salmon - [Download ZIP](downloads/nwb_datasets/chinook.zip)</li>
<li>Chum Salmon - [Download ZIP](downloads/nwb_datasets/chum.zip)</li>
<li>Broad Whitefish - [Download ZIP](downloads/nwb_datasets/whitefish.zip)</li>
<li>Waterfowl - [Download ZIP](downloads/nwb_datasets/waterfowl.zip)</li>
<li>Rusty Blackbird - [Download ZIP](downloads/nwb_datasets/blackbird.zip)</li>
<li>Old-Forest birds - [Download ZIP](downloads/nwb_datasets/forest_birds.zip)</li>
<li>Rusty Blackbird insitu refugia - [Download ZIP](downloads/nwb_datasets/blackbird_insitu_refugia.zip)</li>
<li>Old-Forest Birds insitu refugia - [Download ZIP](downloads/nwb_datasets/forest_birds_insitu_refugia.zip)</li>
</ul>

---

### Ecoregion 3 

```{r echo = FALSE, results = "asis"}
y <- filter(x, Ecoregion=="3")
y <- select(y, -Ecoregion)
kable(y, align="lccc")
```

---

### Ecoregion 12 

```{r echo = FALSE, results = "asis"}
y <- filter(x, Ecoregion=="12")
y <- select(y, -Ecoregion)
kable(y, align="lccc")
```

---

### Ecoregion 13 

```{r echo = FALSE, results = "asis"}
y <- filter(x, Ecoregion=="13")
y <- select(y, -Ecoregion)
kable(y, align="lccc")
```

---

### Ecoregion 14 

```{r echo = FALSE, results = "asis"}
y <- filter(x, Ecoregion=="14")
y <- select(y, -Ecoregion)
kable(y, align="lccc")
```

---

### Ecoregion 15 

```{r echo = FALSE, results = "asis"}
y <- filter(x, Ecoregion=="15")
y <- select(y, -Ecoregion)
kable(y, align="lccc")
```

---

### Ecoregion 17 

```{r echo = FALSE, results = "asis"}
y <- filter(x, Ecoregion=="17")
y <- select(y, -Ecoregion)
kable(y, align="lccc")
```

---

### Ecoregion 18 

```{r echo = FALSE, results = "asis"}
y <- filter(x, Ecoregion=="18")
y <- select(y, -Ecoregion)
kable(y, align="lccc")
```

---

### Ecoregion 21 

```{r echo = FALSE, results = "asis"}
y <- filter(x, Ecoregion=="21")
y <- select(y, -Ecoregion)
kable(y, align="lccc")
```

---

### Ecoregion 22 

```{r echo = FALSE, results = "asis"}
y <- filter(x, Ecoregion=="22")
y <- select(y, -Ecoregion)
kable(y, align="lccc")
```

---

### Ecoregion 23a 

```{r echo = FALSE, results = "asis"}
y <- filter(x, Ecoregion=="23a")
y <- select(y, -Ecoregion)
kable(y, align="lccc")
```

---

### Ecoregion 23b 

```{r echo = FALSE, results = "asis"}
y <- filter(x, Ecoregion=="23b")
y <- select(y, -Ecoregion)
kable(y, align="lccc")
```

---

### Ecoregion 24 

```{r echo = FALSE, results = "asis"}
y <- filter(x, Ecoregion=="24")
y <- select(y, -Ecoregion)
kable(y, align="lccc")
```

---

### Ecoregion 25 

```{r echo = FALSE, results = "asis"}
y <- filter(x, Ecoregion=="25")
y <- select(y, -Ecoregion)
kable(y, align="lccc")
```

---

### Ecoregion 27 

```{r echo = FALSE, results = "asis"}
y <- filter(x, Ecoregion=="27")
y <- select(y, -Ecoregion)
kable(y, align="lccc")
```

---

### Ecoregion 28 

```{r echo = FALSE, results = "asis"}
y <- filter(x, Ecoregion=="28")
y <- select(y, -Ecoregion)
kable(y, align="lccc")
```

---

### Ecoregion 29 

```{r echo = FALSE, results = "asis"}
y <- filter(x, Ecoregion=="29")
y <- select(y, -Ecoregion)
kable(y, align="lccc")
```

---

### Ecoregion 31 

```{r echo = FALSE, results = "asis"}
y <- filter(x, Ecoregion=="31")
y <- select(y, -Ecoregion)
kable(y, align="lccc")
```

---

### Ecoregion 32 

```{r echo = FALSE, results = "asis"}
y <- filter(x, Ecoregion=="32")
y <- select(y, -Ecoregion)
kable(y, align="lccc")
```

---

### Ecoregion 169 

```{r echo = FALSE, results = "asis"}
y <- filter(x, Ecoregion=="169")
y <- select(y, -Ecoregion)
kable(y, align="lccc")
```

---

### Ecoregion 170 

```{r echo = FALSE, results = "asis"}
y <- filter(x, Ecoregion=="170")
y <- select(y, -Ecoregion)
kable(y, align="lccc")
```

---

### Ecoregion 171 

```{r echo = FALSE, results = "asis"}
y <- filter(x, Ecoregion=="171")
y <- select(y, -Ecoregion)
kable(y, align="lccc")
```

---

### Ecoregion 174 

```{r echo = FALSE, results = "asis"}
y <- filter(x, Ecoregion=="174")
y <- select(y, -Ecoregion)
kable(y, align="lccc")
```

---

### Ecoregion 175 

```{r echo = FALSE, results = "asis"}
y <- filter(x, Ecoregion=="175")
y <- select(y, -Ecoregion)
kable(y, align="lccc")
```

---

### Ecoregion 176 

```{r echo = FALSE, results = "asis"}
y <- filter(x, Ecoregion=="176")
y <- select(y, -Ecoregion)
kable(y, align="lccc")
```

---

### Ecoregion 177 

```{r echo = FALSE, results = "asis"}
y <- filter(x, Ecoregion=="177")
y <- select(y, -Ecoregion)
kable(y, align="lccc")
```

---

### Ecoregion 178 

```{r echo = FALSE, results = "asis"}
y <- filter(x, Ecoregion=="178")
y <- select(y, -Ecoregion)
kable(y, align="lccc")
```

---

### Ecoregion 179 

```{r echo = FALSE, results = "asis"}
y <- filter(x, Ecoregion=="179")
y <- select(y, -Ecoregion)
kable(y, align="lccc")
```

---

### Ecoregion 180 

```{r echo = FALSE, results = "asis"}
y <- filter(x, Ecoregion=="180")
y <- select(y, -Ecoregion)
kable(y, align="lccc")
```

---

### Ecoregion 181 

```{r echo = FALSE, results = "asis"}
y <- filter(x, Ecoregion=="181")
y <- select(y, -Ecoregion)
kable(y, align="lccc")
```

---

### Ecoregion 182 

```{r echo = FALSE, results = "asis"}
y <- filter(x, Ecoregion=="182")
y <- select(y, -Ecoregion)
kable(y, align="lccc")
```

---

### Ecoregion 183 

```{r echo = FALSE, results = "asis"}
y <- filter(x, Ecoregion=="183")
y <- select(y, -Ecoregion)
kable(y, align="lccc")
```

